Binning Strategies and Related Loss for Large Data

### 2015-03-03 Paper.Rnw
start of frequency loss subsection

\ktm{When the individual points of a scatterplot are collapsed to bin centers to be displayed as tiles in a binned scatterplot there is a loss of the location information.  This can be expressed as the Euclidean distance between points and the visual center of the tiles (i.e. the bin centers). Note that other distance metrics could be used, but the euclidean distance has a desirable interpretability in $\mathbb{R}^2$. The spatial loss for the $i^{th}$ observation, $L_i^S$ and the total spatial loss, $L^S$ are defined as}
%
\begin{eqnarray}\label{indspatloss}
L_i^S = \sqrt{ (x_i-b_X(x_i))^2 + (y_i-b_Y(y_i))^2 }
\end{eqnarray}
%
\begin{eqnarray}\label{totspatloss}
L^S = \sum_{i=1}^{n} L_i^S
\end{eqnarray}  
%

>>>>

\ktm{When the individual points of a scatterplot are collapsed to bin centers to be displayed as tiles in a binned scatterplot there is a loss of the location information.  This can be expressed as the Euclidean distance between points and the visual center of the tiles (i.e. the bin centers). Note that other distance metrics could be used, but the euclidean distance has a desirable interpretability in $\mathbb{R}^2$. The spatial loss for the $i^{th}$ observation, $L_i^S$ and the total spatial loss, $L^S$ are defined as}
%
\begin{eqnarray}\label{indspatloss}
L_i^S = \sqrt{ (x_i-b_X(x_i))^2 + (y_i-b_Y(y_i))^2 }
\end{eqnarray}
%
\begin{eqnarray}\label{totspatloss}
L^S = \sum_{i=1}^{n} L_i^S
\end{eqnarray}  
%
\ktm{Visual display of spatial loss still needed.}

\subsection{Frequency Loss}

\ktm{If the shading scheme for rendering the counts in each bin is discretized there is a loss of frequency information. While counts can certainly be modeled as continuous on the HSV color space (reference needed) discrete color breaks may be prefered for a few reasons. %The average person is able to  On the continuous scale, a viewer will likely not be able to exactly match a tile shading to the corresponding count on the color key in the legend of the plot without an aid such as interactive mouseover effects. 
}
